### 2020-12-10 paper/localpsf.tex
literature review gah

In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\varphi_i$ and $w_i$ may be arbitrary functions. Product-convolution approximations have been used in a wide variety of fields going back several decades [CITE BIG LIST].
For background on product-convolution approximations, we recommend reading the following excellent papers: [CITES].

@@

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used as an estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. For example, if the width of $\varphi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size. In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method estimates the support of $\varphi_p$ more accurately than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

Matrix-vector products with product-convolution approximations can be performed using the fast Fourier transform if the problem is discretized on a regular grid [CITE]. The product-convolution approximation can then replace the original operator when using Krylov methods to solve linear systems with the original operator as the coefficient operator [CITE]. However, for complex geometries, problems are rarely discretized using regular grids, so we cannot easily use the fast Fourier transform. Furthermore, in big-data inverse problems the Hessian is typically highly ill-conditioned, so the number of Krylov iterations required is large. Thus, after constructing the product-convolution approximation, it is desirable to convert the product-convolution approximation to other matrix formats that are more amenable to linear algebra operations. Wavelet compression methods have been used for this purpose [CITE WAVELETS]. Here we follow our previous work [CITE MY PAPER], in which we converting the product-convolution approximation to H-matrix format.

@@

\subsection{Background}

\subsubsection{Distributions}

@@

\subsubsection{Discretization}
\label{sec:discretization}

@@

>>>>

In general, product-convolution approximations take the form shown in \eqref{eq:product_convolution}, but $\varphi_i$ and $w_i$ may be arbitrary functions. Product-convolution approximations have been used in a wide variety of fields going back several decades [CITE BIG LIST].
For background on product-convolution approximations, we recommend reading the following papers: [CITES].

@@

Our method of estimating the support of the functions $\varphi_i$ was inspired by resolution analysis in seismic imaging [CITE]. In resolution analysis, $\mathcal{A}$ is the Hessian for a seismic inverse problem, and the width of $\varphi_p$ is used to estimate of the minimum length scale on which features of the parameter can be inferred near the point $p$. If the width of $\varphi_p$ is ten meters, then features of the parameter near $p$ can be accurately inferred from data if those features are larger than roughly ten meters in size. In [CITE], the width of $\varphi_x$ is estimated to be the local autocorrelation length of the function $\mathcal{A}^T \zeta$ near $x$, where $\zeta$ is a random noise funtion. In this paper, rather than probing $\mathcal{A}^T$ with random noise functions, we use specific linear and quadratic functions. Our method estimates the support of $\varphi_p$ more accurately than resolution analysis, but our method requires that $\mathcal{A}$ has a positive integral kernel, while the resolution analysis method does not have this requirement.

@@

Matrix-vector products with product-convolution approximations can be performed using the fast Fourier transform if the problem is discretized on a regular grid [CITE]. The product-convolution approximation can then replace the original operator when using Krylov methods to solve linear systems with the original operator as the coefficient operator [CITE]. However, for complex geometries, problems are rarely discretized using regular grids, so we cannot easily use the fast Fourier transform. Furthermore, in big-data inverse problems the Hessian is typically highly ill-conditioned, so the number of Krylov iterations required is large. After constructing the product-convolution approximation, it is therefore desirable to convert the product-convolution approximation to other matrix formats that are more amenable to linear algebra operations. Wavelet compression methods have been used for this purpose [CITE WAVELETS]. Here we follow our previous work [CITE MY PAPER], in which we convert the product-convolution approximation to H-matrix format.

@@

\subsection{Background: distributions}

@@

\subsection{Background: discretization}
\label{sec:discretization}

@@

\subsection{Background: hierarchical matrices}
